Calls vs IMD

### 2021-12-07 output/calls_vs_imd.Rmd
imd stuff

lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
                          pre_post = "Post-COVID"))

@@

  pre_calls <- cheshire_calls %>% 
    filter(incident_type_new == inc_type) %>% 
  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(n = replace_na(n, 0), 
         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))

@@

 p <-  ggplot() + 
  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr, na.rm = TRUE) + 10, label = paste0("n = ",n))) +
  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab(paste0("Number of ",inc_type," calls (per year)")) + 
       scale_y_log10() + 
  theme_bw() + 
  theme(legend.position = c(0.87, 0.75))
 return(p)

@@

pre_calls <- cheshire_calls %>% 
  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
  left_join(., cheshire_imds, by = c( "lsoa" = "LSOA11NM")) %>%
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(n = replace_na(n, 0), 
         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))

@@

ggplot(pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
  geom_boxplot() + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr + 100), label = paste0("n = ",n))) +
  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Number of calls (per year)") + 
  theme_bw() + 
  theme(legend.position = c(0.87, 0.75))

@@

>>>>

lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
                          pre_post = "2020"))

@@

  pre_calls <- cheshire_calls %>% 
    filter(incident_type_new == inc_type) %>% 
  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "2020"), 
         pre_post = factor(pre_post, levels = c("Pre-COVID", "2020")), 
         inc_wk = yearweek(incident_date_time)) %>%  
    group_by(lsoa, pre_post, inc_wk) %>% 
    count() %>% 
    group_by(lsoa, pre_post) %>% summarise(avg_wkly_calls = mean(n, na.rm=TRUE)) %>% 
  left_join(lsoa_filler, .) %>%
    mutate(avg_wkly_calls = replace_na(avg_wkly_calls, 0)) %>% 
    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(avg_wkly_calls = replace_na(avg_wkly_calls, 0))

@@

 p <-  ggplot() + 
  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), 
                                     y = avg_wkly_calls, 
                                     color = factor(pre_post, levels =  c("Pre-COVID", "2020")))) + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, 
                                 y = max(pre_calls$avg_wkly_calls, na.rm = TRUE) + (max(pre_calls$avg_wkly_calls, na.rm = TRUE)/4), 
                                 label = paste0("n = ",n))) +
  labs(title = "Average weekly calls from LSOAs in each IMD decile pre-COVID and 2020") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab(paste0("Average number of ",inc_type," calls (per week)")) + 
  scale_color_brewer("",type = "qual", palette = 2) +  
  theme_bw() + 
  theme(legend.position = c(0.87, 0.75))
 return(p)

@@

pre_calls <- cheshire_calls %>% 
  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "2020"), 
         inc_wk = yearweek(incident_date_time)) %>%   
  group_by(lsoa, pre_post, inc_wk) %>% count() %>% 
  group_by(lsoa, pre_post) %>%  summarise(avg_wk_calls = mean(n, na.rm = TRUE)) %>% 
  left_join(lsoa_filler, .) %>%
    mutate(avg_wk_calls = replace_na(avg_wk_calls, 0)) %>% 
  left_join(., cheshire_imds, by = c( "lsoa" = "LSOA11NM")) %>%
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(avg_wk_calls = replace_na(avg_wk_calls, 0))

@@

ggplot() + 
  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), 
                      y = avg_wk_calls, 
                      color = factor(pre_post, levels =  c("Pre-COVID", "2020")))) + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$avg_wk_calls + 20), label = paste0("n = ",n))) +
  labs(title = "Average weekly calls from LSOAs in each IMD decile pre and post COVID") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Average weekly calls") + 
  theme_bw() + 
  scale_color_brewer("",type = "qual", palette = 2) + 
  theme(legend.position = c(0.87, 0.75))

@@

# What about change over time for each IMD

weekly_count_by_lsoa <- cheshire_calls %>% 
   mutate(inc_wk = yearweek(incident_date_time)) %>%   
   group_by(lsoa, inc_wk) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(n = replace_na(n, 0)) %>% 
  group_by(index_of_multiple_deprivation_imd_decile, inc_wk) %>% 
  summarise(avg_weekly_call = mean(n, na.rm = T), 
            n_per_lsoa = n/n())
# 
# ggplot(weekly_count_by_lsoa, aes(x = inc_wk, y = avg_weekly_call, colour = as.factor(index_of_multiple_deprivation_imd_decile))) +
#   geom_point() + 
#   geom_line()
